### 2019-11-21 1_introduction.tex
Fiddle with figure placement.

Adding a system to Task Bench involves  implementing a set of standard
services, such as executing a task or data transfer, simple enough to 
be implemented with reasonable effort to a level of quality sufficient for comparative
studies. Task Bench provides a core library that encapsulates functionality
shared among systems, which not only reduces implementation effort
but also makes it much easier to achieve truly apples-to-apples comparisons
between systems.

@@

How does one predict whether the performance of a given
system will be good enough for a particular application?
Surprisingly, the most commonly reported performance metrics,
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as increased communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

% Seems to be nearly impossible to get rid of the hyphen, so just give
% up and allow this paragraph to break across it.
\let\oldbrokenpenalty\brokenpenalty
\brokenpenalty=0

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
which are designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s).

\brokenpenalty=\oldbrokenpenalty

@@

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the design of Task Bench. Section~\ref{sec:implementation}
discusses implementations in 15 programming systems.
Section~\ref{sec:metg} defines the METG metric and its
relationship to quantities of interest to application developers.
Section~\ref{sec:evaluation} provides a comprehensive evaluation of
Task Bench on up to 256 Haswell nodes of the Cori
supercomputer~\cite{Cori} (GPU results are reported on Piz Daint~\cite{PizDaint}). Section~\ref{sec:related-work} relates to previous efforts; Section~\ref{sec:conclusion} concludes.

>>>>

Adding a system to Task Bench involves implementing a set of standard
services, such as executing a task or data transfer. Note that, though
the benchmarks are described in terms of task graphs, this is simply a
convenient representation of the computation, and the underlying
system need not provide any native support for tasks. Tasks are simply
coarse units of work; dependencies induce communication. We provide
Task Bench implementations in systems as diverse as MPI and
Spark. Task Bench provides a core API that encapsulates functionality
shared among systems, which reduces implementation effort and makes it
much easier to achieve truly apples-to-apples comparisons between
systems.

@@

How does one predict whether performance will be good enough for a given application?
Surprisingly, the most commonly reported metrics,
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as increased communication) that scale with the number of nodes when
using progressively larger portions of a machine.

@@

% Seems to be nearly impossible to get rid of the hyphen, so just give
% up and allow this paragraph to break across it.
\let\oldbrokenpenalty\brokenpenalty
%% \brokenpenalty=0

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems
listed in Section~\ref{sec:implementation}.
%% :
%% Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP, CUDA),
%% OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
%% PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
%% Spark \cite{Spark10}, StarPU \cite{StarPU11},
%% Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
%% X10 \cite{X1005}.
Using METG, we find that a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While some systems can achieve sub-microsecond METG(50\%) in
best-case scenarios, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. Our study includes several asynchronous systems
which are designed to provide benefits such as overlapped computation
and communication. While small-scale benchmarks of these systems
suffer from increased overhead, we find that the benefits of these systems become
tangible at scale (provided the runtime overhead doesn't increase
beyond about 100~\textmu{}s).

%% \brokenpenalty=\oldbrokenpenalty

@@

% Performance issues:
% Chapel (communication performance, core pinning)
% Dask (asymptotic complexity of dask.delayed)
% PaRSEC (task pruning with non-trivial task graphs)
% Realm (DMA system overhead)
% TensorFlow (constant folding not parallel)

During the development of Task Bench, we have identified performance
bugs in five systems: Chapel, Dask, PaRSEC, Realm and
TensorFlow. Three have been (or are being) fixed and the others have
been acknowledged by the developers of the respective systems. In some
cases these correspond to order of magnitude (or even asymptotic)
improvements in the performance of the underlying systems---benefits
which apply well beyond Task Bench to all classes of applications.

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the Task Bench design. Section~\ref{sec:implementation}
discusses implementations in 15 systems.  Section~\ref{sec:metg}
defines METG and its relationship to quantities of interest to
application developers.  Section~\ref{sec:evaluation} provides a
comprehensive evaluation on the Cori
supercomputer~\cite{Cori}. Section~\ref{sec:related-work} relates to
previous efforts; Section~\ref{sec:conclusion} concludes.

### 2019-11-21 t2_parameters.tex
Edits from Sean.
Edit the introduction to make some points more clear.

height & height of graph & number of timesteps \\
width & width of graph & degree of parallelism \\
dependence & trivial, stencil, etc. & dependence relation \\
kernel & compute, memory, etc. & type of kernel \\
output & bytes per dependency & degree of comm.
\end{tabular}

\vspace{1em}

Options specific to dependence relations:

\begin{tabular}{l | l | l}
Parameter & Valid For & Purpose \\
\hline
radix & nearest & dependencies per task
\end{tabular}

\vspace{1em}

Options specific to kernels:

\begin{tabular}{l | l | l}
Parameter & Valid For & Purpose \\
\hline
iterations & compute, memory & task duration/problem size \\
span & memory & bytes used per task per iter. \\
scratch & memory & total working set size \\
imbalance & load imbalanced & degree of imbalance
\end{tabular}

\caption{Task Bench parameters.\label{tab:parameters}}
\vspace{-0.5cm}
\end{table}

>>>>

height & height of graph & number of timesteps \\
width & width of graph & degree of parallelism \\
dependence & trivial, stencil, etc. & communication pattern \\
\quad \raisebox{0.35ex}{$\llcorner$} radix & \quad (for nearest pattern) & dependencies per task \\
kernel & compute, memory, etc. & type of kernel \\
\quad \raisebox{0.35ex}{$\llcorner$} iter. & \quad (for all kernels) & task duration \\
\quad \raisebox{0.35ex}{$\llcorner$} span & \quad (for memory kernel) & bytes used per task per iter. \\
\quad \raisebox{0.35ex}{$\llcorner$} scratch & \quad (for memory kernel) & total working set size \\
\quad \raisebox{0.35ex}{$\llcorner$} imbal. & \quad (for load imbalance) & degree of imbalance \\
output & bytes per dependency & degree of comm.
\end{tabular}

\caption{Task Bench parameters.\label{tab:parameters}}
\vspace{-0.75cm}
\end{table}
